Design and Implementation of Probabilistic Programming Language Anglican

### 2016-08-03 paper/paper.tex
update

While probabilistic programming systems shorten the iteration cycle in
exploratory model design, they typically lack basic functionality needed for
data I/O, pre-processing, and analysis and visualization of inference results.
In this demonstration, we describe the implementation of
Anglican~(\cite{TMW15, Anglican}), a probabilistic
programming language that tightly integrates with
Clojure~\cite{H08,Clojure}, a general-purpose programming language
that runs on the Java Virtual Machine (JVM). Both languages share a common
syntax, and can be invoked from each other. This allows Anglican programs to
make use of a rich set of libraries written in both Clojure and Java.
Conversely Anglican allows intuitive and compact specification of models for
which inference may be performed as part of a larger Clojure project.

@@

>>>>

While probabilistic programming systems shorten the iteration cycle in
exploratory model design, they typically lack basic functionality needed for
data I/O, pre-processing, and analysis and visualization of inference results.
In this demonstration, we describe the implementation of
Anglican~\cite{TMW15, Anglican}, a probabilistic
programming language that tightly integrates with
Clojure~\cite{H08,Clojure}, a general-purpose programming language
that runs on the Java Virtual Machine (JVM). Both languages share a common
syntax, and can be invoked from each other. This allows Anglican programs to
make use of a rich set of libraries written in both Clojure and Java.
Conversely Anglican allows intuitive and compact specification of models for
which inference may be performed as part of a larger Clojure project.

@@

\hy{Great introduction. It very nicely explains why Anglican
is born and how it is implemented. If I act as a really picky
reviewer or a reader, I would also expect the instroduction
to help me grasp in a high level what new insights or scientific problems 
this development of Anglican have resulted in or solved so far.}
